Finding Maximum $k$-Cliques Faster using Lazy Global Domination

### 2016-04-12 paper/paper.tex
Missing words

We selected the four graphs which we were unable to solve (for some values of $k$), along with two
of the challenging graphs which required substantial amounts of search (at least half a million
nodes) to solve, and repeated the experiments using parallel search with 20 threads and the
domination rule (with the laziness made thread-safe) enabled, using the resplitting strategy
described by \citeauthor{DBLP:journals/topc/McCreeshP15} \shortcite{DBLP:journals/topc/McCreeshP15}.
The results are shown in \cref{table:parallel}. Parallel search allowed us to close two more
instances, and improved the bounds on ?? further instances with 12 hours of search. However, to get
sufficient work balance, we had to allow for work splitting to depth 10 rather than depth 3. A close
inspection of the search patterns showed that simpler static decomposition approaches
\cite{DBLP:journals/jcisd/DepolliKRTJ13,DBLP:journals/cor/SegundoLP16} would give little to no
speedup on many harder $k$-clique instances, unless it were somehow possible to generate
$\mathcal{O}(|V|^{10})$ subproblems.

@@

On the other hand, for ``wing-nodal'' with $k=4$, the parallel run did much less work than the
sequential run: a speedup of over 100 was obtained from 20 cores. A similar effect occurred with
``cond-mat'' and $k=4$, and on ?? of the graphs where the incumbent was improved, it was improved
after less time than the sequential runs took. This is because the work splitting mechanism we used
explicitly diversifies at the top of search first, where branching heuristics are least likely to be
correct, which leads to an initial incumbent being found faster---this is in line with recent
observations that tailored work stealing should be favoured over randomised work stealing for
combinatorial search problems \cite{DBLP:conf/cp/ChuSS09,DBLP:journals/topc/McCreeshP15}.

>>>>

We selected the four graphs which we were unable to solve (for some values of $k$), along with two
of the challenging graphs which required substantial amounts of search (at least half a million
nodes) to solve, and repeated the experiments using parallel search with 20 threads and the
domination rule (with the laziness made thread-safe) enabled, using the resplitting strategy
described by \citeauthor{DBLP:journals/topc/McCreeshP15} \shortcite{DBLP:journals/topc/McCreeshP15}.
The results are shown in \cref{table:parallel}. Parallel search allowed us to close two more
instances, and gave improved bounds on the four remaining instances within 12 hours. However, to
get sufficient work balance, we had to allow for work splitting to depth 10 rather than depth 3. A
close inspection of the search patterns showed that simpler static decomposition approaches
\cite{DBLP:journals/jcisd/DepolliKRTJ13,DBLP:journals/cor/SegundoLP16} would give little to no
speedup on many harder $k$-clique instances, unless it were somehow possible to generate
$\mathcal{O}(|V|^{10})$ subproblems.

@@

On the other hand, for ``wing-nodal'' with $k=4$, the parallel run did much less work than the
sequential run: a speedup of over 100 was obtained from 20 cores. A similar effect occurred with
``cond-mat'' and $k=4$. This is because the work splitting mechanism we used explicitly diversifies
at the top of search first, where branching heuristics are least likely to be correct, which leads
to an initial incumbent being found faster---this is in line with recent observations that tailored
work stealing should be favoured over randomised work stealing for combinatorial search problems
\cite{DBLP:conf/cp/ChuSS09,DBLP:journals/topc/McCreeshP15}.
